Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-28 manuscript/manuscript.Rmd
cross refs

This time series is representative of the patterns observed in the data (see App. \ref{app:tbd}).
The episode reward and episode length statistics are shown in Fig. \ref{fig:rew_len_fig}.
There, we highlight two things:
First, that the tendency towards early episode ends is fixed by the conservative approach of fishing at 80% of the optimal mortality rate.
(In App. \ref{app:tbd} we discuss a warning about this approach, however: the arbitrarily chosen percentage itself lives on a ‘‘knife's edge.’’
More concretely, choosing a higher percentage, say 90%, can switch the behaviour of the controlled system and give rise to the proliferation of early episode ends.)
Second, that while the conservative 80% approach has a stable behavior, it consistently produces smaller harvests than a DRL generated policy.

@@

Notice the anti-correlation between $X$ and $Y$ along the paths, this is especially prominent for the constant mortality plots.
This anti-correlation is, furthermore, observed in the time series plots (see Fig. \ref{fig:timeseries} and App. \ref{app:tbd}).

@@

# Appendix A: collected time series data

@@

```{r} 
#| label: timeseries_msy
#| fig.cap: "Nine time series of the system controlled by the MSY constant mortality policy." 
#| out.width: "6.5in"
msy_tac_ppo |> 
    group_by(rep) |>
    filter(rep < 9, policy == "msy") |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(rep)) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 0.6)
```

```{r} 
#| label: timeseries_tac
#| fig.cap: "Nine time series of the system controlled by the policy using 80 percent of the MSY constant mortality." 
#| out.width: "6.5in"
msy_tac_ppo |> 
    group_by(rep) |>
    filter(rep < 9, policy == "tac") |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(rep)) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 0.6)
```

```{r} 
#| label: timeseries_ppo
#| fig.cap: "Nine time series of the system controlled by the trained DRL agent." 
#| out.width: "6.5in"
msy_tac_ppo |> 
    group_by(rep) |>
    filter(rep < 9, policy == "ppo") |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(rep)) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 0.6)
```

# Appendix B: Conservative scale-downs of MSY

>>>>

This time series is representative of the patterns observed in the data (see App. A).
The episode reward and episode length statistics are shown in Fig. \ref{fig:rew_len_fig}.
There, we highlight two things:
First, that the tendency towards early episode ends is fixed by the conservative approach of fishing at 80% of the MSY mortality rate.
(In App. B we discuss and evaluate other policies using a fixed-percentage of the MSY mortality rate.)
Second, that while the conservative 80% approach has a stable behavior, it consistently produces smaller harvests than a DRL generated policy.

@@

Notice the anti-correlation between $X$ and $Y$ along the paths, this is especially prominent for the constant mortality plots.
This anti-correlation is, furthermore, observed in the time series plots (see Fig. \ref{fig:timeseries} and App. A).

@@

\appendix

# Appendix

## Collected time series data

@@

```{r} 
#| label: timeseries_msy
#| fig.cap: "Nine time series of the system controlled by the MSY constant mortality policy." 
#| out.width: "6.5in"
msy_tac_ppo |> 
    group_by(rep) |>
    filter(rep < 9, policy == "msy") |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(rep)) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 0.5)
```

```{r} 
#| label: timeseries_tac
#| fig.cap: "Nine time series of the system controlled by the policy using 80 percent of the MSY constant mortality." 
#| out.width: "6.5in"
msy_tac_ppo |> 
    group_by(rep) |>
    filter(rep < 9, policy == "tac") |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(rep)) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 0.5)
```

```{r} 
#| label: timeseries_ppo
#| fig.cap: "Nine time series of the system controlled by the trained DRL agent." 
#| out.width: "6.5in"
msy_tac_ppo |> 
    group_by(rep) |>
    filter(rep < 9, policy == "ppo") |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(rep)) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 0.5)
```

## Conservative scale-downs of MSY
